HO unification from object language to meta language

### 2024-02-23 paper/main.tex
refactor eta expand rule in elpi and tex
update constructor name
tex update

\begin{figure}[H]
  \begin{elpicode}
    kind tm type.
    type app list tm -> tm.
    type lam (tm -> tm) -> tm.
    type c   string -> tm.
  \end{elpicode}
  \caption{Common terms}
  \label{code:common-terms}
  \Description[code:common-terms]{code:common-terms}
\end{figure}
%
\noindent
This encoding is very similar to the one introduced in \cref{sec:intro},\todo{say we do not care about types} except
for the \elpiIn{all} constructor. We explicitly neglect it since blabla.
Moreover, since we are working with unification variables we need to introduce a
new constructor.

@@

\subsection{Term equality}

@@

\begin{figure}
  \begin{elpicode}
    % congruence
    type ~(\Eo)~ tm -> tm -> o.
    app L1 ~\Eo~app L2 :- forall2 ~(\Eo)~ L1 L2.
    lam F1 ~\Eo~lam F2 :- pi x\ x ~\Eo~x => F1 x ~\Eo~F2 x.
    con X ~\Eo~con X.
    fov N ~\Eo~fov N.
    % eta
    lam F ~\Eo~T :- not (T = lam _), 
      pi x\ beta T [x] (T' x), lam F ~\Eo~lam T'.
    T ~\Eo~(lam F) :- not (T = lam _), 
      pi x\ beta T [x] (T' x), lam T' ~\Eo~lam F.
    % beta
    app [lam X | TL] ~\Eo~T :- beta (lam X) TL T', T' ~\Eo~T.
    T ~\Eo~app [lam X | TL] :- beta (lam X) TL T', T ~\Eo~T'.
  \end{elpicode}
  \caption{Equal predicate}
  \label{code:eq-pred}
  \Description[code:equal-pred]{code:equal-pred}
\end{figure}

>>>>

\begin{figure}[H]
  \begin{elpicode}
    kind tm type.
    type app list tm -> tm.
    type lam (tm -> tm) -> tm.
    type con string -> tm.
  \end{elpicode}
  \caption{Common terms}
  \label{code:common-terms}
  \Description[code:common-terms]{code:common-terms}
\end{figure}
%
\noindent
This encoding is very similar to the one introduced in \cref{sec:intro},\todo{say we do not care about types} except
for the \elpiIn{all} constructor. We explicitly neglect it since blabla.
Moreover, since we are working with unification variables we need to introduce a
new constructor.

@@

\subsection{Auxiliary relations}

Together with the description of the terms of the language, we need some
auxiliary functions to perform operations like term equality, unification,
dereferencing. There predicates are supposed to be implemented in the OL and the
ML following respectively their specification. In the following few paragraphs
we give a brief definition of them.

\paragraph{Term equality: \Eo vs. \Ee}
\paragraph{Term unification: \Uo vs. \Ue}
\paragraph{Term dereferencing: $\rho s$ vs. $\sigma t$}
TODO

@@

\begin{figure}
  \begin{elpicode}
    % congruence
    type ~(\Eo)~ tm -> tm -> o.
    app L1 ~\Eo~app L2 :- forall2 ~(\Eo)~ L1 L2.
    lam F1 ~\Eo~lam F2 :- pi x\ x ~\Eo~x => F1 x ~\Eo~F2 x.
    con X ~\Eo~con X.
    fov N ~\Eo~fov N.
    % eta
    lam F ==o T :- pi x\ beta T [x] (T' x), 
      x ==o x => F x ==o T' x.
    T ==o lam F :- pi x\ beta T [x] (T' x), 
      x ==o x => T' x ==o F x.
    % beta
    app [lam X | TL] ~\Eo~T :- beta (lam X) TL T', T' ~\Eo~T.
    T ~\Eo~app [lam X | TL] :- beta (lam X) TL T', T ~\Eo~T'.
  \end{elpicode}
  \caption{Equal predicate}
  \label{code:eq-pred}
  \Description[code:equal-pred]{code:equal-pred}
\end{figure}
